\textbf{NBA Party}

### 2017-04-07 init_model.rnw
Using nmusicians interacted with ndays.lgame == 1, we get a significant model (p = 0.0014) and a modest success rate on hold-out data (55%).

<<echo=F,results='hide'>>=
require(data.table)
require(ggplot2)
load(file = 'tmp_data/covers_lines.RData')
lines[, `:=`(pct = NULL, weekend = NULL)]
others <- grep("party", names(lines), value = T, invert = T)
setcolorder(lines, c(others, c('party')))
@

>>>>

<<echo=F,results='hide'>>=

### Reshape data
### One model, outcome ~ loast.game.llocation, last.city.size, last.city.region,

### Group data by region.

require(data.table)
require(ggplot2)
require(magrittr)
require(sampling)
set.seed(4052017)

load(file = 'tmp_data/covers_lines.RData')
load(file = 'tmp_data/ndrink_estabs.RData')

lines <- merge(lines, drinks, 
               by.x = c('season', 'last.game.loc'),
               by.y = c('season', 'team'), all.x = T)

m <- glm(outcome == 'W' ~ I(nmusicians*(ndays.lgame==1)), 
         data = lines[season < 2017 & last.game.loc != team])
p <- predict(m, newdata = lines[season == 2017 & ndays.lgame == 1 & last.game.loc != team], type = 'response')
table(round(p), lines[season == 2017 & ndays.lgame == 1 & last.game.loc != team, outcome])

## lines = lines[team != last.game.loc]
lines[, `:=`(pct = NULL, weekend = NULL)]

melted = melt(lines, id.vars = c('season', 'date', 'location'))
setkey(melted, season, date, location)
melted = melted[variable == 'team']
casted = dcast(melted, formula = season + date + location ~ .)

valid.idx = which(lines$season == 2017) %>% sample(., size = floor(length(.) / 12))
valid = lines[valid.idx]
lines = lines[-valid.idx]

n = length(unique(lines$last.game.loc))
m = length(unique(lines$season))
setkey(lines, season, last.game.loc, date)

### Stratified random sampling.
s = strata(data = lines, stratanames = c('season', 'last.game.loc'),
           size = rep(7, n*m), method = 'srswor')

### Partition data for two-stage least-squares.
var.creation.indices = s$ID_unit
var.creation = lines[var.creation.indices]
training     = lines[-var.creation.indices]

### First stage model.
coefs <- sapply(1:60, function(x) {
    indices = sample(1:nrow(var.creation), size = nrow(var.creation), replace = T)
    glm(outcome == 'W' ~ 0 + last.game.loc, 
        data = var.creation[indices], family = 'binomial')$coef
})

rownames(coefs) <- gsub('last.game.loc', '', rownames(coefs))
coef = data.table(last.game.loc = rownames(coefs), coef = rowMeans(coefs))

## m = glm(outcome == 'W' ~ 0 + last.game.loc, 
##         data = var.creation[last.game.loc != team], 
##         family = 'binomial')
## coef <- m$coef
## names(coef) <- gsub('last.game.loc', '', names(coef))
## coef = data.table(last.game.loc = names(coef), coef)

setkey(training, last.game.loc)
training = training[coef]

### Second stage model.
m = glm(outcome == 'W' ~ 1 + I(coef*(ndays.lgame==1)),
        data = training[last.game.loc != team], 
        family = 'binomial', subset = season < 2017) # Significant.

### Meet the spread on 2017 data vs. prediction.
setkey(valid, last.game.loc)
valid = valid[coef]
preds = predict(m, newdata = valid[ndays.lgame == 1], type = 'response')
table(round(preds), valid[ndays.lgame == 1, outcome])

## ggplot(actual, aes(x = meet.spread, y = preds, label = last.game.loc)) + 
##     geom_point()+
##     geom_label()

### Not quite worth betting on, yet.
## yhat <- predict(m, newdata = training[season >= 2017 & ndays.lgame == 1], type = 'response') %>% round
## table(yhat, training[season >= 2017 & ndays.lgame==1, outcome])
